\documentclass{article}

\usepackage[pdftex]{graphicx}
\usepackage{siunitx}

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.



% *** MATH PACKAGES ***
%
\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath






% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

%\usepackage[utf8]{inputenc}
%\usepackage{helvet}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
%\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}
%\usepackage{url}
%\usepackage{amstext}

%\bibliographystyle{IEEEtran}

% Title Page
\title{Recurrence Quantification Analysis for Sentinel-1 time series of land surfaces}
\author{Felix Cremer, Mikhail Urbazaev, Christiane Schmullius and Christian Thiel}

%\IEEEauthorblockA{Chair of Earth Observation, Friedrich-Schiller University, Jena,Germany\\
%Email: felix.cremer@uni-jena.de}

\begin{document}
\maketitle
%\tableofcontents
\begin{abstract}

%Keywords:Recurrence, SAR, time series, remote sensing
%
\end{abstract}
\section{Introduction}
With the launch of the Sentinel-1 A (April 2014) and Sentinel-1 B (April 2016) Satellites of the European Space Agency (ESA) there is an unprecedented number of C-Band SAR acquisitions available.
The combination of Sentinel-1 A and Sentinel-1 B result in time series with a repetition rate of 6 days under the same acquisition conditions
and up to daily repetitions with the combination of all available acquisitions over one region of interest.
Describe why we do land use mapping
To further use these datasets, one can do feature selection via the computation of multitemporal metrics for every pixel.



\section{Method}

Recurrence plots have been proposed by Eckmann et al 1987. They are method to visualize the recurrences of a time series. They are a quadratic matrix which entries are defined as follows:
$$R_{i,j} = \Theta(\epsilon - \lvert x_i - x_j \rvert), i,j = 1,...,N$$

\section{Experimental Results}
\subsection{Data and Preprocessing}
\color{red}{
The proposed method was tested on a stack of 53 Sentinel-1 GRD images of the same relative orbit collected over Central Germany (close to Erfurt)
at flat terrain (mean slope $\ang{3.44} \pm \ang{3.38}$) between October 2014 and July 2018.
The time span between the acquisitions was 12 days for most of the images.
Exceptions include a gap of 48 days at the beginning of the time series and eight gaps of 24 days.
Figure \ref{study_area} shows one image of the temporal stack.
}
\color{red}{
The data have been preprocessed using the SNAP software \cite{SNAP}.
The single time steps are multilooked to a \SI{10}{\m} x \SI{10}{\m} pixel spacing.
The orthorectification is based on the original orbit state vectors and the \SI{30}{\m} SRTM digital elevation model\cite{SRTM}.
The preprocessing also included radiometric terrain flattening after \cite{Small} which results in $\gamma^0$ backscatter values.
All images were coregistered in the DEM geometry after geocoding to achieve a subpixel coregistration precision which is of eminent importance when the pixels are investigated in the temporal domain only.
}



\subsection{Separability analysis}


\section{Discussion}


\section{Summary and Conclusion}



\section*{Acknowledgment}
This work was funded by the DLR in the Sentinel4REDD project (FKZ:50EE1540).
This work uses Copernicus Sentinel data 2014-2018.



\bibliography{literatur}

\end{document}
